Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
finer stroke for Fig 5

\subsubsection*{MFCCs \vs scattering}
As shown in Figure, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
Not only the average accuracy is improved, but the variance between fold-wise accuracies is also reduced, \eg from $16\%$ to $7\%$ in the case of early integration.
This is in accordance with the previous results on similarity retrieval, as well as with other papers comparing mel-frequency coefficients with scattering coefficients on a variety of tasks, ranging from musical genre recognition \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) with a Gaussian radial kernel.
See text for details.}
\end{center}
\ref{fig:folds}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.}
\end{center}
\end{table}

>>>>

\subsubsection*{MFCCs \vs scattering}
As shown in Figure \cite{folds}, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
Not only the average accuracy is improved, but the variance between fold-wise accuracies is also reduced, \eg from $16\%$ to $7\%$ in the case of early integration.
This is in accordance with the previous results on similarity retrieval, as well as with other papers comparing mel-frequency coefficients with scattering coefficients on a variety of tasks, ranging from musical genre recognition \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.
See text for details.}
\end{center}
\ref{fig:folds}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.}
\end{center}
\ref{table:dcase2013}
\end{table}
